Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2017-01-04 document/submission/ms.tex
Addressing the referee comments

Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process. In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.  We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.  Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, with a best-fit filling factor of $\sim80$\%  for the cool photosphere at the time of the observation.  These results are supported by comparisons of this mix of hot and cool photospheric temperatures by analyses of the spectral energy distribution, rotational modulation of colors and of TiO band strengths, and low-resolution optical/near-IR spectroscopy.  LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.  The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates and naively using the same model tracks.  Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters. We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra, and anti-correlations expected in the velocity jitter of the warm and cool components.

\end{abstract}

@@

\maketitle

\section{Introduction}\label{sec:intro}

The causes of age uncertainties and of large luminosity spreads in young clusters are controversial \citep[see reviews by][]{preibisch12,soderblom14}.  Absolute ages are usually inferred from comparisons between observed stellar properties and pre-main sequence evolutionary models, which are sensitive to stellar birthlines and the input physics that controls the contraction and internal heating.  Within clusters, any real differences in ages between stars may be masked by observational uncertainties in temperature and luminosity measurements \citep[e.g.][]{hartmann01,slesnick08}.

@@

\input{tbl_best_fit.tex}[!b]

>>>>

Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process. In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.  We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.  Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, with a best-fit filling factor of $\sim80$\%  for the cool photosphere at the time of the observation.  These results are supported by comparisons of this mix of hot and cool photospheric temperatures by analyses of the spectral energy distribution, rotational modulation of colors and of TiO band strengths, and low-resolution optical/near-IR spectroscopy.  LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.  The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates and naively using the same model tracks.  Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters. In some spectral regions starspots acts as a featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.  Evidence for anti-correlations in velocity of the the warm and cool components is found.
\end{abstract}

@@

\maketitle
\section{Introduction}\label{sec:intro}
The causes of age uncertainties and of large luminosity spreads in young clusters are controversial \citep[see reviews by][]{preibisch12,soderblom14}.  Absolute ages are usually inferred from comparisons between observed stellar properties and pre-main sequence evolutionary models, which are sensitive to stellar birthlines and the input physics that controls the contraction and internal heating.  Within clusters, any real differences in ages between stars may be masked by observational uncertainties in temperature and luminosity measurements \citep[e.g.][]{hartmann01,slesnick08}.

@@

\input{tbl_best_fit.tex}
